Hemispheric Lateralization in ICH

### 2023-06-02 code/dataAnalysis/02analysis.qmd
changes

gmrs90 <- ggplot(
  data = mrsCounts,
  aes(x = ichLaterality, y = percentPatients, fill = forcats::fct_rev(mrs90))
) +
  geom_bar(stat = "identity", position = "fill", width = 0.5) +
  geom_text(aes(label = patients),
    position = position_stack(vjust = 0.5),
    color = "white",
    size = 5,
    family = "FigTree"
  ) +
  coord_flip() +
  scale_y_continuous(
    name = NULL,
    labels = scales::percent_format(accuracy = 1),
    breaks = c(seq(0, 1, 0.2))
  ) +
  scale_x_discrete(name = NULL) +
  scale_fill_manual(values = myColors, breaks = c(0, 1, 2, 3, 4, 5, 6)) +
  labs(
    title = "90 days") +
  theme(
    plot.title = element_text(face = "bold", size = 20, lineheight = 0.1),
    plot.subtitle = element_text(size = 20, lineheight = 0.1),
    plot.caption = element_text(size = 20),
    plot.title.position = "plot",
    plot.caption.position = "plot",
    legend.title = element_blank(),
    legend.position = "right",
    legend.text = element_text(size = 15, lineheight = 0.5),
    # legend.margin = margin(r = 50),
    panel.grid.minor.x = element_blank(),
    panel.grid.major.y = element_blank(),
    axis.text.y = element_text(size = 20, lineheight = 0.5, margin = margin(r = -10)),
    axis.title.x = element_text(size = 20, lineheight = 0.5)
  )

@@

gmrs180 <- ggplot(
  data = mrsCounts,
  aes(x = ichLaterality, y = percentPatients, fill = forcats::fct_rev(mrs180))
) +
  geom_bar(stat = "identity", position = "fill", width = 0.5) +
  geom_text(aes(label = patients),
    position = position_stack(vjust = 0.5),
    color = "white",
    size = 5,
    family = "FigTree"
  ) +
  coord_flip() +
  scale_y_continuous(
    name = NULL,
    labels = scales::percent_format(accuracy = 1),
    breaks = c(seq(0, 1, 0.2))
  ) +
  scale_x_discrete(name = NULL) +
  scale_fill_manual(values = myColors, breaks = c(0, 1, 2, 3, 4, 5, 6)) +
  labs(
    title = "180 days") +
  theme(
    plot.title = element_text(face = "bold", size = 20, lineheight = 0.1),
    plot.subtitle = element_text(size = 20, lineheight = 0.1),
    plot.caption = element_text(size = 20),
    plot.title.position = "plot",
    plot.caption.position = "plot",
    legend.title = element_blank(),
    legend.position = "right",
    legend.text = element_text(size = 15, lineheight = 0.5),
    # legend.margin = margin(r = 50),
    panel.grid.minor.x = element_blank(),
    panel.grid.major.y = element_blank(),
    axis.text.y = element_text(size = 20, lineheight = 0.5, margin = margin(r = -10)),
    axis.title.x = element_text(size = 20, lineheight = 0.5)
  )

@@

gmrs365 <- ggplot(
  data = mrsCounts,
  aes(x = ichLaterality, y = percentPatients, fill = forcats::fct_rev(mrs365))
) +
  geom_bar(stat = "identity", position = "fill", width = 0.5) +
  geom_text(aes(label = patients),
    position = position_stack(vjust = 0.5),
    color = "white",
    size = 5,
    family = "FigTree"
  ) +
  coord_flip() +
  scale_y_continuous(
    name = NULL,
    labels = scales::percent_format(accuracy = 1),
    breaks = c(seq(0, 1, 0.2))
  ) +
  scale_x_discrete(name = NULL) +
  scale_fill_manual(values = myColors, breaks = c(0, 1, 2, 3, 4, 5, 6)) +
  labs(
    title = "365 days") +
  theme(
    plot.title = element_text(face = "bold", size = 20, lineheight = 0.1),
    plot.subtitle = element_text(size = 20, lineheight = 0.1),
    plot.caption = element_text(size = 20),
    plot.title.position = "plot",
    plot.caption.position = "plot",
    legend.title = element_blank(),
    legend.position = "right",
    legend.text = element_text(size = 15, lineheight = 0.5),
    panel.grid.minor.x = element_blank(),
    panel.grid.major.y = element_blank(),
    axis.text.y = element_text(size = 20, lineheight = 0.5, margin = margin(r = -10)),
    axis.title.x = element_text(size = 20, lineheight = 0.5)
  )

mrsCombined <- 
(gmrs90 + theme(plot.margin = unit(c(50,0,75,0), "pt"))) / (gmrs180 + theme(plot.margin = unit(c(0,0,75,0), "pt"))) / (gmrs365 + theme(plot.margin = unit(c(0,0,75,0), "pt"))) +
  plot_annotation(title = 'ICH Laterality and modified Rankin Scale',
                theme = theme(plot.title = element_text(face = "bold", size = 35, lineheight = 0.1))) +
  plot_layout(guides = 'collect') & theme(legend.position='right', legend.direction="vertical")

@@

ggplot(
  data = euroQOLCounts,
  aes(x = ichLaterality, y = percentPatients, fill = fct_rev({{ euroSelfCare365 }}))
) +
  geom_bar(stat = "identity", position = "fill", width = 0.5) +
  geom_text(aes(label = percentPatientsLabel),
    position = position_stack(vjust = 0.5),
    color = "white",
    size = 5) +
  coord_flip() +
  scale_y_continuous(
    name = NULL,
    labels = scales::percent_format(accuracy = 1),
    breaks = c(seq(0, 1, 0.2))
  ) +
  scale_x_discrete(name = NULL) +
  scale_fill_manual(values = myColors, breaks = legendLabels) +
  labs(
    title = plotTitle) +
  theme(
    plot.title = element_text(face = "bold", size = 20, lineheight = 0.1),
    plot.subtitle = element_text(size = 20, lineheight = 0.1),
    plot.caption = element_text(size = 20),
    plot.title.position = "plot",
    plot.caption.position = "plot",
    legend.title = element_blank(),
    legend.position = "bottom",
    legend.text = element_text(size = 15, lineheight = 0.5),
    panel.grid.minor.x = element_blank(),
    panel.grid.major.y = element_blank(),
    axis.text.y = element_text(size = 20, lineheight = 0.5, margin = margin(r = -10)),
    axis.title.x = element_text(size = 20, lineheight = 0.5)
  )
}
legendLabels <- c("No Problems", "Some Problems", "Confined to Bed")
ggeuroMobility90 <- euroQolPlot(euroMobility90, legendLabels, "EuroQOL Mobility")

@@

euroQolCombined90 <- 
(ggeuroMobility90 + theme(plot.margin = unit(c(50,0,75,0), "pt"))) / (ggeuroSelfCare90 + theme(plot.margin = unit(c(0,0,75,0), "pt"))) / (ggeuroUsual90 + theme(plot.margin = unit(c(0,0,75,0), "pt"))) /
(ggeuroPain90 + theme(plot.margin = unit(c(0,0,75,0), "pt"))) / 
(ggeuroAnxiety90 + theme(plot.margin = unit(c(0,0,75,0), "pt"))) +
  plot_annotation(title = 'ICH Laterality and HRQOL at 90 days',
                theme = theme(plot.title = element_text(face = "bold", size = 35, lineheight = 0.1)))
  # plot_layout(guides = 'collect') & theme(legend.position='right', legend.direction="vertical")

euroQolCombined180 <- 
(ggeuroMobility180 + theme(plot.margin = unit(c(50,0,75,0), "pt"))) / (ggeuroSelfCare180 + theme(plot.margin = unit(c(0,0,75,0), "pt"))) / (ggeuroUsual180 + theme(plot.margin = unit(c(0,0,75,0), "pt"))) /
(ggeuroPain180 + theme(plot.margin = unit(c(0,0,75,0), "pt"))) / 
(ggeuroAnxiety180 + theme(plot.margin = unit(c(0,0,75,0), "pt"))) +
  plot_annotation(title = 'ICH Laterality and HRQOL at 180 days',
                theme = theme(plot.title = element_text(face = "bold", size = 35, lineheight = 0.1)))
  # plot_layout(guides = 'collect') & theme(legend.position='right', legend.direction="vertical")

euroQolCombined365 <- 
(ggeuroMobility365 + theme(plot.margin = unit(c(50,0,75,0), "pt"))) / (ggeuroSelfCare365 + theme(plot.margin = unit(c(0,0,75,0), "pt"))) / (ggeuroUsual365 + theme(plot.margin = unit(c(0,0,75,0), "pt"))) /
(ggeuroPain365 + theme(plot.margin = unit(c(0,0,75,0), "pt"))) / 
(ggeuroAnxiety365 + theme(plot.margin = unit(c(0,0,75,0), "pt"))) +
  plot_annotation(title = 'ICH Laterality and HRQOL at 365 days',
                theme = theme(plot.title = element_text(face = "bold", size = 35, lineheight = 0.1)))
  # plot_layout(guides = 'collect') & theme(legend.position='right', legend.direction="vertical")

@@

euroVASplot <- function(x, title) {
  d |>
  ggplot(aes({{x}}, fill = ichLaterality)) +
  geom_density(color = NA, alpha = 0.8) +
  labs(title = {{ title }},
        x = NULL,
        y = NULL) +
  theme(
  plot.title = element_text(face = "bold", size = 20, lineheight = 0.1),
  plot.subtitle = element_text(size = 20, lineheight = 0.1),
  plot.caption = element_text(size = 20),
  plot.title.position = "plot",
  plot.caption.position = "plot",
  legend.title = element_blank(),
  legend.position = "bottom",
  legend.text = element_text(size = 15, lineheight = 0.5),
  panel.grid.minor.x = element_blank(),
  panel.grid.major.y = element_blank(),
  axis.text.y = element_text(size = 20, lineheight = 0.5, margin = margin(r = -10)),
  axis.title.x = element_text(size = 20, lineheight = 0.5)
  )
}

@@

ggeuroVASCombined <- 
(ggeurovas90 + theme(plot.margin = unit(c(50,0,75,0), "pt"))) / (ggeurovas180 + theme(plot.margin = unit(c(0,0,75,0), "pt"))) / (ggeurovas365 + theme(plot.margin = unit(c(0,0,75,0), "pt"))) +
  plot_annotation(title = 'ICH Laterality EuroQOL VAS',
                theme = theme(plot.title = element_text(face = "bold", size = 35, lineheight = 0.1)))

>>>>

gmrs90 <- ggplot(
  data = mrsCounts,
  aes(x = ichLaterality, y = percentPatients, fill = forcats::fct_rev(mrs90))
) +
  geom_bar(stat = "identity", position = "fill", width = 0.5) +
  geom_text(aes(label = patients),
    position = position_stack(vjust = 0.5),
    color = "white",
    size = 5,
    family = "FigTree"
  ) +
  coord_flip() +
  scale_y_continuous(
    name = NULL,
    labels = scales::percent_format(accuracy = 1),
    breaks = c(seq(0, 1, 0.2))
  ) +
  scale_x_discrete(name = NULL) +
  scale_fill_manual(values = myColors, breaks = c(0, 1, 2, 3, 4, 5, 6)) +
  labs(
    title = "90 days"
  ) +
  theme(
    plot.title = element_text(face = "bold", size = 20, lineheight = 0.1),
    plot.subtitle = element_text(size = 20, lineheight = 0.1),
    plot.caption = element_text(size = 20),
    plot.title.position = "plot",
    plot.caption.position = "plot",
    legend.title = element_blank(),
    legend.position = "right",
    legend.text = element_text(size = 15, lineheight = 0.5),
    # legend.margin = margin(r = 50),
    panel.grid.minor.x = element_blank(),
    panel.grid.major.y = element_blank(),
    axis.text.y = element_text(size = 20, lineheight = 0.5, margin = margin(r = -10)),
    axis.title.x = element_text(size = 20, lineheight = 0.5)
  )

@@

gmrs180 <- ggplot(
  data = mrsCounts,
  aes(x = ichLaterality, y = percentPatients, fill = forcats::fct_rev(mrs180))
) +
  geom_bar(stat = "identity", position = "fill", width = 0.5) +
  geom_text(aes(label = patients),
    position = position_stack(vjust = 0.5),
    color = "white",
    size = 5,
    family = "FigTree"
  ) +
  coord_flip() +
  scale_y_continuous(
    name = NULL,
    labels = scales::percent_format(accuracy = 1),
    breaks = c(seq(0, 1, 0.2))
  ) +
  scale_x_discrete(name = NULL) +
  scale_fill_manual(values = myColors, breaks = c(0, 1, 2, 3, 4, 5, 6)) +
  labs(
    title = "180 days"
  ) +
  theme(
    plot.title = element_text(face = "bold", size = 20, lineheight = 0.1),
    plot.subtitle = element_text(size = 20, lineheight = 0.1),
    plot.caption = element_text(size = 20),
    plot.title.position = "plot",
    plot.caption.position = "plot",
    legend.title = element_blank(),
    legend.position = "right",
    legend.text = element_text(size = 15, lineheight = 0.5),
    # legend.margin = margin(r = 50),
    panel.grid.minor.x = element_blank(),
    panel.grid.major.y = element_blank(),
    axis.text.y = element_text(size = 20, lineheight = 0.5, margin = margin(r = -10)),
    axis.title.x = element_text(size = 20, lineheight = 0.5)
  )

@@

gmrs365 <- ggplot(
  data = mrsCounts,
  aes(x = ichLaterality, y = percentPatients, fill = forcats::fct_rev(mrs365))
) +
  geom_bar(stat = "identity", position = "fill", width = 0.5) +
  geom_text(aes(label = patients),
    position = position_stack(vjust = 0.5),
    color = "white",
    size = 5,
    family = "FigTree"
  ) +
  coord_flip() +
  scale_y_continuous(
    name = NULL,
    labels = scales::percent_format(accuracy = 1),
    breaks = c(seq(0, 1, 0.2))
  ) +
  scale_x_discrete(name = NULL) +
  scale_fill_manual(values = myColors, breaks = c(0, 1, 2, 3, 4, 5, 6)) +
  labs(
    title = "365 days"
  ) +
  theme(
    plot.title = element_text(face = "bold", size = 20, lineheight = 0.1),
    plot.subtitle = element_text(size = 20, lineheight = 0.1),
    plot.caption = element_text(size = 20),
    plot.title.position = "plot",
    plot.caption.position = "plot",
    legend.title = element_blank(),
    legend.position = "right",
    legend.text = element_text(size = 15, lineheight = 0.5),
    panel.grid.minor.x = element_blank(),
    panel.grid.major.y = element_blank(),
    axis.text.y = element_text(size = 20, lineheight = 0.5, margin = margin(r = -10)),
    axis.title.x = element_text(size = 20, lineheight = 0.5)
  )

mrsCombined <-
  (gmrs90 + theme(plot.margin = unit(c(50, 0, 75, 0), "pt"))) / (gmrs180 + theme(plot.margin = unit(c(0, 0, 75, 0), "pt"))) / (gmrs365 + theme(plot.margin = unit(c(0, 0, 75, 0), "pt"))) +
    plot_annotation(
      title = "ICH Laterality and modified Rankin Scale",
      theme = theme(plot.title = element_text(face = "bold", size = 35, lineheight = 0.1))
    ) +
    plot_layout(guides = "collect") & theme(legend.position = "right", legend.direction = "vertical")

@@

  ggplot(
    data = euroQOLCounts,
    aes(x = ichLaterality, y = percentPatients, fill = fct_rev({{ euroSelfCare365 }}))
  ) +
    geom_bar(stat = "identity", position = "fill", width = 0.5) +
    geom_text(aes(label = percentPatientsLabel),
      position = position_stack(vjust = 0.5),
      color = "white",
      size = 5
    ) +
    coord_flip() +
    scale_y_continuous(
      name = NULL,
      labels = scales::percent_format(accuracy = 1),
      breaks = c(seq(0, 1, 0.2))
    ) +
    scale_x_discrete(name = NULL) +
    scale_fill_manual(values = myColors, breaks = legendLabels) +
    labs(
      title = plotTitle
    ) +
    theme(
      plot.title = element_text(face = "bold", size = 20, lineheight = 0.1),
      plot.subtitle = element_text(size = 20, lineheight = 0.1),
      plot.caption = element_text(size = 20),
      plot.title.position = "plot",
      plot.caption.position = "plot",
      legend.title = element_blank(),
      legend.position = "bottom",
      legend.text = element_text(size = 15, lineheight = 0.5),
      panel.grid.minor.x = element_blank(),
      panel.grid.major.y = element_blank(),
      axis.text.y = element_text(size = 20, lineheight = 0.5, margin = margin(r = -10)),
      axis.title.x = element_text(size = 20, lineheight = 0.5)
    )
}
legendLabels <- c("No Problems", "Some Problems", "Confined to Bed")
ggeuroMobility90 <- euroQolPlot(euroMobility90, legendLabels, "EuroQOL Mobility")

@@

euroQolCombined90 <-
  (ggeuroMobility90 + theme(plot.margin = unit(c(50, 0, 75, 0), "pt"))) / (ggeuroSelfCare90 + theme(plot.margin = unit(c(0, 0, 75, 0), "pt"))) / (ggeuroUsual90 + theme(plot.margin = unit(c(0, 0, 75, 0), "pt"))) /
  (ggeuroPain90 + theme(plot.margin = unit(c(0, 0, 75, 0), "pt"))) /
  (ggeuroAnxiety90 + theme(plot.margin = unit(c(0, 0, 75, 0), "pt"))) +
  plot_annotation(
    title = "ICH Laterality and HRQOL at 90 days",
    theme = theme(plot.title = element_text(face = "bold", size = 35, lineheight = 0.1))
  )
# plot_layout(guides = 'collect') & theme(legend.position='right', legend.direction="vertical")

euroQolCombined180 <-
  (ggeuroMobility180 + theme(plot.margin = unit(c(50, 0, 75, 0), "pt"))) / (ggeuroSelfCare180 + theme(plot.margin = unit(c(0, 0, 75, 0), "pt"))) / (ggeuroUsual180 + theme(plot.margin = unit(c(0, 0, 75, 0), "pt"))) /
  (ggeuroPain180 + theme(plot.margin = unit(c(0, 0, 75, 0), "pt"))) /
  (ggeuroAnxiety180 + theme(plot.margin = unit(c(0, 0, 75, 0), "pt"))) +
  plot_annotation(
    title = "ICH Laterality and HRQOL at 180 days",
    theme = theme(plot.title = element_text(face = "bold", size = 35, lineheight = 0.1))
  )
# plot_layout(guides = 'collect') & theme(legend.position='right', legend.direction="vertical")

euroQolCombined365 <-
  (ggeuroMobility365 + theme(plot.margin = unit(c(50, 0, 75, 0), "pt"))) / (ggeuroSelfCare365 + theme(plot.margin = unit(c(0, 0, 75, 0), "pt"))) / (ggeuroUsual365 + theme(plot.margin = unit(c(0, 0, 75, 0), "pt"))) /
  (ggeuroPain365 + theme(plot.margin = unit(c(0, 0, 75, 0), "pt"))) /
  (ggeuroAnxiety365 + theme(plot.margin = unit(c(0, 0, 75, 0), "pt"))) +
  plot_annotation(
    title = "ICH Laterality and HRQOL at 365 days",
    theme = theme(plot.title = element_text(face = "bold", size = 35, lineheight = 0.1))
  )
# plot_layout(guides = 'collect') & theme(legend.position='right', legend.direction="vertical")

@@

euroVASplot <- function(x, title) {
  d |>
    ggplot(aes({{ x }}, fill = ichLaterality)) +
    geom_density(color = NA, alpha = 0.8) +
    labs(
      title = {{ title }},
      x = NULL,
      y = NULL
    ) +
    theme(
      plot.title = element_text(face = "bold", size = 20, lineheight = 0.1),
      plot.subtitle = element_text(size = 20, lineheight = 0.1),
      plot.caption = element_text(size = 20),
      plot.title.position = "plot",
      plot.caption.position = "plot",
      legend.title = element_blank(),
      legend.position = "bottom",
      legend.text = element_text(size = 15, lineheight = 0.5),
      panel.grid.minor.x = element_blank(),
      panel.grid.major.y = element_blank(),
      axis.text.y = element_text(size = 20, lineheight = 0.5, margin = margin(r = -10)),
      axis.title.x = element_text(size = 20, lineheight = 0.5)
    )
}

@@

ggeuroVASCombined <-
  (ggeurovas90 + theme(plot.margin = unit(c(50, 0, 75, 0), "pt"))) / (ggeurovas180 + theme(plot.margin = unit(c(0, 0, 75, 0), "pt"))) / (ggeurovas365 + theme(plot.margin = unit(c(0, 0, 75, 0), "pt"))) +
  plot_annotation(
    title = "ICH Laterality EuroQOL VAS",
    theme = theme(plot.title = element_text(face = "bold", size = 35, lineheight = 0.1))
  )
